Airspace configuration decision based on Monte-Carlo tree search

### 2018-01-30 article/article.tex
(+) intro finished

The sequence of configurations will be represented as a tree. The resulting
sequence will therefore be a path from the root to a leaf of this tree. This
problem is highly combinatorial (partitioning of the airspace). Knowing that a
sochastic tree search algorithm has been honing from a good Go
player~\cite{gelly2012go} to the best one with AlphaGo.

>>>>

The sequence of configurations will be represented as a tree. The resulting
sequence will therefore be a path from the root to a leaf of this tree. This
problem is highly combinatorial (partitioning of the airspace). Knowing that a
sochastic tree search algorithm has been honing from a good
player~\cite{gelly2012go} to the best one with AlphaGo on one of the most highly
combinatorial game wich is the game of Go entices us to use one for this
problem. The Monte Carlo tree search~\cite{browne2012survey} algorithm will be
used to fullfill this task.

\section{Previous related works}
\label{sec:previous_related_works}
